Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-10 hotstorage13/eval.tex
new dat

The total local disk space usage for each machine is 8.05GB:  5.75GB for global index partitions with 10 snapshots per VM
and 2.3GB for accumulated requests.
Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
block-wise full deduplication removes about additional 74.5\% of duplicates.
The final content copied to the backup storage is reduced by 94.4\% in total.

@@

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
the memory limit imposed on each node varies  from 20MB to 200MB.
The overall processing time does not have a significant reduction as we increase to 200MB.
The parallel time includes the first scanning time, 
of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The total time is mainly dominated by  the two scans of dirty VM segments.
The time for copying to the final backup storage is overlapped with VM scanning.
%Each scan takes about 1.4 hours.
The aggregated throughput is  about 8GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 3.09 hours with the very small resource usage.
As we vary the cluster size and the number of VMs for backup remains a constant (25),
the processing time and throughput do not change much. Thus the aggregated throughput
scales up linearly.

Table~\ref{tab:overall} shows memory usage and performance when 30MB memory limit is imposed and
the number of parititons per machine ($q$) varies from 50 to 1500.
Row 2 shows the memory usage required to load a partition of global index and detection requests,
varying from 161MB to 5.3MB. With  30MB memory limit,  $q=50$ would not be a viable choice.
Row 3 is the total time and Row 4 is  the aggregated throughput of  100 nodes.
%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
%with the very small resource usage.
Row 5 is  the parallel time if  we use Option 1 with $p\times q$ send buffers 
described in Section~\ref{sect:arch}. 
With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
a big increase of IO requests and seek cost.

>>>>

The total local disk usage on
each machine is about 8GB for duplicate detection purpose and most of them for global index. 
Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
block-wise full deduplication removes about additional 74.5\% of duplicates.
The final content copied to the backup storage is reduced by 94.4\% in total.

@@

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
the memory limit imposed on each node varies  from 20MB to 200MB.
The overall processing time does not have a significant reduction as we increase to 200MB.
The parallel time includes the first scanning time, 
of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The total time is mainly dominated by  the two scans of dirty VM segments.
The time for copying to the final backup storage is overlapped with VM scanning.
%Each scan takes about 1.4 hours.
The aggregated throughput is  about 9.6GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 2.9 hours with the very small resource usage.
As we vary the cluster size and the number of VMs for backup remains a constant (25),
the processing time and throughput do not change much. Thus the aggregated throughput
scales up linearly.

Table~\ref{tab:overall} shows memory usage and performance when 35MB memory limit is imposed and
the number of parititons per machine ($q$) varies from 50 to 1500.
Row 2 shows the memory usage required to load a partition of global index and detection requests,
varying from 156MB to 5.2MB. With  35MB memory limit,  $q=50$ would not be a viable choice.
Row 3 is the total time and Row 4 is  the aggregated throughput of  100 nodes.
%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
%with the very small resource usage.
Row 5 is  the parallel time if  we use Option 1 with $p\times q$ send buffers 
described in Section~\ref{sect:arch}. 
With the large number of buffers, the available space per buffer reduces significantly as $q$ increases, which leads to
a big increase of IO requests and seek cost.
